\chapter{Material and Methods}
\section{Plant Materials}
In this study, the plant we use is \textit{Arabidopsis thaliana}. The plant seeds are harvested in the plant growth chamber in the University of Manchester. Some \textit{Arabidopsis} mutants are oreded from Norttingham Arabidopsis Stock Centre (NASC). The mutants we used are listed in Table :\\

\begin{tabular}[h]{|c|c|c|}
		\hline
		\textsf{\textbf{Salk \textnumero}} & \textsf{\textbf{Name}} & \textsf{\textbf{Description}}\\
		\hline
		Salk\_002316 & ire1$\alpha$A & IRE1$\alpha$ mutant, heterozygous \\
		\hline
		Salk\_050203C & bz60 & bzip60 mutant, homozygous \\
		\hline
		Salk\_132285C & bz28A & bzip28 mutant, homozygous \\
		\hline
		Salk\_114900C & bz28B & bzip28 mutant, homozygous \\
		\hline
		Salk\_0180112C & ire1$\alpha$B & IRE1$\alpha$ mutant, homozygous \\
		\hline
\end{tabular}
\linebreak
\linebreak
\section{Plant Growth Conditions}
For preparation of the seeds, wash \textit{Arabidopsis} seeds in a clean 1.5mL Eppendorf tube with 70\% ethanol for 10 minutes. Then discard 70\% ethanol by pipetting and dry for 5 minutes. Then add 0.2\% agar into the tube and mix the seeds well.\\
Store the seeds mixed with 0.2\% agar in dark at 4\textcelsius~for vernalisation. The length of vernalisation lasts 48 hours. \\
Spread the seeds on a 1/2 MS with phytagel plate by using pipette before putting into plant growth cabinet (SANYO). The temperature for germination is 22\textcelsius. All-day light is applied, the intensity of light is ().\\
1/2 MS Phytagel is prepared as the following table: \\

\begin{tabular}{c c}
	\hline
	\textsf{\textbf{Components}} & \textsf{\textbf{Component Added(1L)}} \\
	\hline
	MS medium with Gamborg & 4.33g \\
	Phytagel & 6.5g\\
	MES Hydrated & 1.0g \\
	\hline
\end{tabular}
\linebreak
\linebreak
Use 900mL of dd\ce{H2O} to dissolve and adjust the pH value to 5.7, then add 100mL more \ce{H2O} to make the final volume to 1L. Autoclave the medium before using.\\
For soil cultivation, transfer seedlings into soil after 7 days growth on the plate. 
\section{Chemical Reagents}
\begin{longtable}{L{8cm} R{5cm}}
\textopenbullet~Luria Broth (Miller's LB) powder & (Sigma-Aldrich) \\
\textopenbullet~Murashige \& Skoog (MS) medium with Gamborg \ce{B5} Vitamins & (Duchefa Biochemie)\\
\textopenbullet~Super Optimal broth with Catabolite repression (S.O.C) medium & (CloneTech) \\
\textopenbullet~Agar (Baterial biological grade) & (Formedium) \\
\textopenbullet~Phytagel & (Sigma-Aldrich) \\
\textopenbullet~Agarose (Molecular Grade) & (Bioline) \\
\textopenbullet~Tunicamycin & (Sigma-Aldrich) \\
\textopenbullet~Kanamycin Sulfate & (CALBIOCHEM) \\
\textopenbullet~Gentamycin & (Sigma-Aldrich) \\
\textopenbullet~Ampicilin & (Sigma-Aldrich) \\
\textopenbullet~Bovine Serum Albumin (BSA) & (Sigma-Aldrich) \\
\textopenbullet~Macerozyme & (YAKULT) \\
\textopenbullet~Cellullase & (YAKULT) \\
\textopenbullet~\ce{3,3'}-Diaminobenzidine (DAB) & (Sigma-Aldrich) \\
\textopenbullet~Dithiothreitol (DTT) & (Melford) \\
\textopenbullet~Phosphate Buffered-Saline (PBS) tablet & (Fisher) \\
\textopenbullet~Tris-\ce{HCl} (Molecular Biology Grade) & (Promega) \\
\textopenbullet~Tris-Base & (Fisher) \\
\textopenbullet~Quick Start Bradford 1$\times$ Dye Reagent & (Bio-Rad) \\
\textopenbullet~Pierce 660nm Protein Assay Reagent & (Thermo-Scientific) \\
\textopenbullet~Tetramethylethylenediamine (TEMED) & (Fluka) \\
\textopenbullet~Polysorbate 20 (TWEEN 20) & (Sigma-Aldrich) \\
\textopenbullet~2-($N$-morpholino)ethanesulfonic acid (MES) Hydrated & (Sigma-Aldrich) \\
\textopenbullet~Phenylmethanesulfonyl fluoride (PMSF) & (Sigma-Aldrich) \\
\textopenbullet~Trypan blue & (Sigma-Aldrich) \\
\textopenbullet~Ponceau S & (Sigma-Aldrich) \\
\end{longtable}

\section{Commercialised Kit}
\begin{longtable}[h]{|l|c|}
	\hline
	\textsf{\textbf{Kit Name}} & \textsf{\textbf{Provider\textfractionsolidus Company}} \\
	\hline
	GeneJET Plant RNA Purification Mini Kit & Thermo Scientific \\
	\hline
	GeneJET Plasmid Miniprep Kit & Thermo Scientific \\
	\hline
	Monarch Plasmid Miniprep Kit & New England Biology \\
	\hline
	NucleoSpin Plant II & Macherey-Nagel \\
	\hline
	NucleoSpin Gel \& PCR Clean-up & Macherey-Nagel \\
	\hline
	DreamTaq Green PCR Master Mix (2$\times$)  & Thermo-Scientific \\
	\hline
	KAPA HiFi HotStart PCR Kit & KAPABiosystems \\
	\hline
	RQ1 RNase-Free DNase Kit & Promega \\
	\hline
	High-Capacity cDNA Reverse Transcription Kit & Applied Biosystems \\
	\hline
	SensiFAST SYBR Hi-ROX (2$\times$) Kit & Bioline \\
	\hline
	Stellar Competent Cell Kit & CloneTech \\
	\hline
	Gateway LR Clonase II Enzyme mix kit & Invitrogen \\
	\hline
	Gateway BP Clonase II Enzyme mix kit & Invitrogen \\
	\hline
\end{longtable}
\section{Devices}

	\begin{longtable}{ |L{3cm}|C{4cm}|C{6.5cm}|}
		\hline
		\textsf{\textbf{Device/Facility}} & \textsf{\textbf{Device Name}} & \textsf{\textbf{Manufacturer}} \\
		\hline
		Plant Grwoth Cabinet & Percival Scientific & AR-66L2 Arabidopsis growth chamber \\
		\hline
		Plant Grwoth Cabinet & Percival Scientific & CLF PlantMaster Plant Growth Complex\\
		\hline
		Seedling Growth Cabinet & SANYO & MLR-350 Versatile Environmental Test Chamber \\
		\hline
		Fume hood & Cenvair (UK) & HLF horizontal unidirectional airflow cabinet \\
		\hline
		Fume hood & S+B & Ecoline Fume Cupboards \\
		\hline
		Thermal Incubator & Laboratory Thermal Equipment & \\
		\hline
		Desiccator & NALGENE & 5311-0250 Vacuum Desiccator \\
		\hline 
		Shaker & New Brunswick Scientific & C25 Incubator Shaker \\
		\hline
		Mini shaker & Stuart Scientific & SSM1 Mini orbital shaker \\
		\hline
		Rotator & Stuart Scientific & SB2 Tube rotator \\
		\hline
		Vortex machine & Scientific Industries & Vortex-Genie (G560)SI-0246 2 Shaker \\
		\hline
		Vortex machine & Labinco Laboratory Equipment & L46 Tube vortex mixer \\
		\hline
		pH meter & METTLER\&TOLEDO & MP220 Basic pH\textfractionsolidus mV\textfractionsolidus \textcelsius ~Meter \\
		\hline
		Conductivity meter & HORIBA Scientific & LAQUAtwin B\_771 COND \\
		\hline
		Stirrer & Stuart & SB161 Magnetic Stirrer \\
		\hline
		Spinner & Labnet & Spectrafuge mini C1301 \\
		\hline
		Centrifuge & eppendorf & 5417R Refrigirated Microcentrifuge Centrifuge \\
		\hline
		Centrifuge & eppendorf & 5424 Microcentrifuge \\
		\hline
		Centrifuge & eppendorf & 5702 R refrigerated centrifuge \\
		\hline
		Centrifuge & Hermle LaborTechnik &  Z300K Universal Centrifuge \\
		\hline
		UV-Vis Spectrophotometer & ThermoFischer Scientific  & NanoDrop 2000c \\
		\hline
		UV-Vis Spectrometer & Eppendorf  & BioPhotometer \\
		\hline
		RT-PCR machine & Applied Biosystems & ABI PRISM 7000 \\
		\hline
		RT-PCR machine & ThermoFischer Scientific & StepOnePlus Real-Time PCR systme \\
		\hline
		PCR machine & G-Storm &  GS4822 PCR system \\
		\hline
		Water Bath & Grant & GD100 Thermostatic Control Unit \\
		\hline
		Dry Bath Incubator & Starlab & N2400-4001 Dry Bath Heating System \\
		\hline
		Electrophoresis Chambers & Bio-Rad & Mini-PROTEAN III Handcast Systems \\
		\hline
		Electrophoresis Power supply & Bio-Rad & PowerPac Basic Power Supply Device\\
		\hline
		Gel Imaginger & Bio-Rad & Gel Doc XR+ System \\
		\hline
	\end{longtable}


\section{Primer List}
Here are the primers mentioned in this theses. \\
\linebreak
\begin{longtable}{| C{4cm} | c | L{5cm} |}
	\hline
	\textsf{\textbf{Target Gene}} & \textsf{\textbf{Name}} & \textsf{\textbf{Sequence}} \\
	\hline
	\multirow{2}{*}{UBC21} & UBQ21\_409F & ACAGCGAGAGAAAGTAGCAGA\\
	 & UBQ21\_489R & TTGATAAGAGCGGTCCATTTGAA \\
	\hline
	\multirow{2}{*}{18S} & 18S\_29F & GGTCTGTGATGCCCTTAGATGTT \\
	 & 18S\_102R & GGCAAGGTGTGAACTCGTTGA \\
	\hline
	\multirow{2}{*}{bZIP60 (Unspliced)} & q\_bz60\_u\_f & AAGCAGGAGTCTGCTGTGCTCTTG \\
	 & q\_bz60\_r & CCCGAGCCCGTTTAGAAC \\
	\hline
	\multirow{4}{*}{bZIP60 (Spliced)} & q\_bz60\_s\_f & AAGCAGGAGTCTGCTGTTGGGTTC \\
	 & q\_bz60\_s\_f2 & CGAAGCAGGAGTCTGCTGTTGG \\
	 & q\_bz60\_s\_f3 & GAAGCAGGAGTCTGCTGTTGGG \\
	 & q\_bz60\_r & CCCGAGCCCGTTTAGAAC \\
	\hline
	\multirow{2}{*}{BIP1} & AtBIP1\_F & TGTGAAAGCAGAGGACAAGG\\
	 & AtBIP1\_R & ACCATCCGGTCAATCTCTTC \\
	\hline
	\multirow{2}{*}{BIP2\textfractionsolidus3} & AtBIP3\_F & TGAGCCTTTAACGAGAGCAA \\
	 & AtBIP3\_F & CCGCATCTTTAAGAGCCTTC \\
	\hline
	\multirow{2}{*}{Meta\_Caspase5} & MC5\_v4\_F & AGAGAAACATCACTGAGCTGATTGA \\
	 & MC5\_v4\_R & TCAACAATGCCCTTCGAATATTC \\
	\hline
	\multirow{2}{*}{bZIP28} & bZ28\_rt\_f & ATGTCACTACCCACGGCAAG \\
	 & bZ28\_rt\_r & GAGCGTCTTTGTTTGGCTGG \\
	\hline
	\multirow{3}{*}{bZIP28} & AtBZIP28\_1642F & GGCTCAGGGCCACTAATGGATTAC \\
	 & AtBZIP28\_1864F & CTTTGTTTGGCTGGGTTCCG \\
	 & AtBZIP28\_1735R & TGCTGGAGACTGATGACGGGACTA \\
	\hline
	\multirow{2}{*}{bZIP49} & bZ49\_rt\_f & TGATCCCAGAGAAGGCGGTA \\
	 & bZ49\_rt\_r & CCGTCCACAAGCACGACTAT \\
	\hline
	\multirow{2}{*}{bZIP17} & bZ17\_rt\_f & ATACCCCTGCACTGCCTCTA \\
	 & bZ17\_rt\_r & CACCGTTGGCTGCTTTTGTT \\
	\hline
	 & Oligo dT & TTT-TTT-TTT-TTT-TTT-TTT \\
	\hline
	 & pDONR201\textfractionsolidus207\_seq\_F & TCGCGTTAACGCTAGCATGGATCTC \\
	\hline
	mGFP &  attB1\_mGFP & GGGGACAAGTTTGTACAAAAAAGCAGGCTATATGAGTAAAGGAGAAGAACT \\
	\hline
	mGFP & attB2\_mGFP & GGGGACCACTTTGTACAAGAAAGCTGGGTCTTTGTATAGTTCATCCATGC \\
	\hline
	NAC089 & attB1\_ANAC089 & GGGGACAAGTTTGTACAAAAAAGCAGGCTAT ATGGACACGAAGGCGGTTGG \\
	\hline
	NAC089 & attB2\_ANAC089 & GGGGACCACTTTGTACAAGAAAGCTGGGTCTTATTCTAGATAAAACAACA \\
	\hline
	NAC089 & NAC089\_down\_test\_F & TCTCGATGAAGCGGTGATGACAGGG \\
	\hline
	mGFP, NAC089 & ANAC089\_mGFP\_f
	 & ATGTTGTTTTATCTAGAAAGTAAAGGAGAAGAACTTTTCACTGGAGT \\
	\hline
	mGFP, NAC089 & mGFP\_ANAC089\_r & AAGTTCTTCTCCTTTACTTTCTAGATAAAACAACATTGCTATCAGAGC \\
	\hline	
\end{longtable}

All the primers are synthesised and provided from Eurogentec company. 

\section{PCR}
\subsection{Probing PCR}
For basic PCR test, we use DreamTaq DNA polymerase (2$\times$) (Thermo-Scientific). Each PCR is carried out in a 200$\mu$L PCR tube (StarLab) with the total volume of 20$\mu$L. \\

\begin{tabular}{l r}
	\hline
	\textsf{\textbf{Reagent}} & \textsf{\textbf{Volume}} \\
	\hline
	DreamTaq Green PCR (2$\times$) Master Mix & 10.0 $\mu$ L \\
	Forward primer (10$\mu$M) & 1.0$\mu$L \\
	Reverse primer (10$\mu$M) & 1.0$\mu$L \\
	Template DNA & (50-200ng)  \\
	dd\ce{H2O} & (to 20.0$\mu$L)\\
	\hline
\end{tabular}
\linebreak
\linebreak
The reaction condition is described in the following table: \\

\begin{tabular}[H]{l c c  c}
	\hline
	~~~ & \textsf{\textbf{Temperature (\textcelsius)}} &  \textsf{\textbf{Lasting Time}}  &\\
	\hline
	Initial denaturation &  95 &  5 min  &\\
	\hline
	Denaturation  &  95 &  30 sec  & \multirow{3}{*}{35 Cycles} \\
	Annealing &  60 &  1 min per 1kb  & \\
	Extension &  72 & 90 sec &\\
	\hline
	Final extension &  72 & 10 min &\\
	Storing &  4 & $\infty$ &\\
	\hline
\end{tabular}
\linebreak
\linebreak
PCR product can be directly used for agarose gel electrophoresis. 
\subsection{Colony PCR}

\subsection{High fidelity PCR}
Use KAPA HiFi HotStart ReadyMix Kit (KAPABiosystems) for high fidelity required gene sequence amplification. \\
One whole reaction is prepared in 25$\mu$L. \\

\begin{tabular}{l r} 
	\hline
	\textsf{\textbf{Reagent}} & \textsf{\textbf{Volume}} \\
	\hline
	KAPA HiFi HotStart 2$\times$ ReadyMix & 12.5$\mu$L \\
	Forward primer (10$\mu$M) & 0.75$\mu$L \\
	Reverse primer (10$\mu$M) & 0.75$\mu$L \\
	Template DNA & (50-100ng)  \\
	dd\ce{H2O} & (to 25.0$\mu$L)\\
	\hline
\end{tabular}
\linebreak
\linebreak
The reaction condition is described in the following table: \\

\begin{tabular}[H]{l c c  c}
\hline
~~~ & \textsf{\textbf{Temperature (\textcelsius)}} &  \textsf{\textbf{Lasting Time}}  &\\
\hline
Initial denaturation &  95 &  3 min  &\\
\hline
Denaturation  &  98 &  20 sec  & \multirow{3}{*}{32 Cycles} \\
Annealing &  60 &  15 sec  & \\
Extension &  72 & 90 sec &\\
\hline
Final extension &  72 & 30 min &\\
Storing &  4 & $\infty$ &\\
\hline
\end{tabular}
\linebreak
\linebreak
The PCR product can be directly used for agarose gel electrophoresis by mixing with 5$\times$ DNA loading buffer (Bioline). 
\subsection{Agarose Gel Electrophoresis}
All the gel used in our experiments are 1\%(w\textfractionsolidus v) agarose gel. Add agarose (bioline) into 0.5$\times$TBE buffer and dissolve by heating in microwave oven. Add 1$\mu$L SafeView nucleic acid stain (NBS Biological) in each 30mL agarose gel. Run the gel in 0.5$\times$TBE buffer for 1 hour with the voltage of 50V. Use Gel Doc XR+ System (Bio-Rad) to take photo of the electrophoresis result.\\
TBE buffer is prepared as 5$\times$ stock for better stability and dilute 10 times for use. \\

\begin{tabular}{c c}
	\hline
	\textbf{\textsf{Components}} & \textbf{\textsf{Final Concentration (5$\times$)}} \\
	\hline
	Tris-Base & 0.45M \\
	Boric acid & 0.45M \\
	EDTA & 0.01M \\
	\hline
\end{tabular}
\linebreak
\linebreak

\subsection{RT-PCR}
RT-PCR experiments are performed on ABI Prism 7000 Sequence Detecting Systems (Applied Biosystems) and StepOne Plus Real-Time PCR System (ThermoFischer). The enzyme used in RT-PCR reactions is Sensi-FAST SYBR Hi-ROX kit (BIOLINE). We apply 4-points standard curve for calculating the amplification efficiency by using Arabidopsis genomic DNA ladder with the copy number from 50000 to 50. We use triplicates for each sample. The whole reaction system is kept at 12$\mu$L. All the components are listed in the following table.\\

\begin{tabular}{l r} 
	\hline
	\textsf{\textbf{Reagent}} & \textsf{\textbf{Volume}} \\
	\hline
	\textsf{Sensi-FAST\texttrademark~ SYBR\textsuperscript{\textregistered}} 2$\times$ Master Mix & 6.0$\mu$L \\
	Forward primer (10$\mu$M) & 0.5$\mu$L \\
	Reverse primer (10$\mu$M) & 0.5$\mu$L \\
	Template cDNA & (100~200ng)  2.0$\mu$L \\
	dd\ce{H_2O} & (to 12.0$\mu$L)  3.0$\mu$L \\
	\hline
\end{tabular}
\linebreak
\linebreak
The RT-PCR reaction condition setting: pre-heat the 96 well plate to 50\textcelsius for 2 minutes, then to 95\textcelsius, hold for 10 minutes. After pre-heating step, the samples are amplified in 40 cycles, which include denaturation (95\textcelsius~for 15 seconds) and annealing (60\textcelsius~for 1 minute). In dissociation stage, we apply 95\textcelsius~for 15 seconds, 60\textcelsius~for 20 seconds and finally 95\textcelsius~for another 15 seconds.\\

\section{Total RNA Extraction}
\subsection{Arabidopsis Seedling RNA Extraction}
Collect the arabidopsis seedlings ($\geqslant$30 seedlings) in a 1.5mL Eppendorf Tube. Store at -80\textcelsius~for at least 1 day before using. Grind the seedlings with sterilised pellet pestles and then add 500$\mu$L of RNAzol and 200$\mu$L of dd\ce{H_2O}. Vortex for 15 seconds to mix completely. Then leave at room temperature for 15 minutes before centrifuging at room temperature, 12000 rpm. Collect the supernatant and add the equal volumn of 100\% isopropanol. Centrifuge another 10 minutes at room temperature, 12000 rpm and then use 75\% ethanol to wash the pellet 3 times. Remove 75\% ethanol and air-dry the pellet for 15 minutes. Finally add 50$\mu$L RNase free water and vortex for 5 minutes to completely dissolve the RNA pellet.\\
\subsection{Arabidopsis Leaf RNA Extraction} 
Collect the leaf sample (100$\mu$g to 1mg) in a 1.5mL Eppendorf Tube, and store at -80\textcelsius for at least 1 day. For extracting the RNA, grind the leaf sample with sterilised pellet pestle. Then process with GeneJET Plant RNA Purification Kit (ThermoFischer).\\

\section{cDNA Synthesis}
cDNA samples are synthesised from the total RNA (1$\mu$g). Use RQ1 RNase-Free DNase (Promega) to treat the RNA samples, for 30 minutes at 37\textcelsius. Then add RQ1 Stop Solution (Promega) to incubate at 65\textcelsius~for 20 minutes. RNA reverse transcription is done with Maxima H Minus Reverse Transcriptase kit (ThermoFischer) and Oligo dT primers. The amplification conditions are \\
\linebreak
\begin{tabular}[H]{c c c c c}
	\hline
	~~~ & &\textsf{\textbf{Temperature (\textcelsius)}} & ~~~ & \textsf{\textbf{Lasting Time (min)}} \\
	\hline
	Step 1 & & 25 & & 10 \\
	Step 2 & & 50 & & 15 \\
	Step 3 & & 85 & & 5 \\
	\hline
\end{tabular}
\linebreak
\linebreak
Then make 10 times dilution for RT-PCR usage. The Minus RT control samples are prepared using the same method, only without adding RNA reverse transcriptase.

\section{Baterial Transformation}
The bacteria strain for used is Stellar competent \textit{E.coli} cell (CloneTech).
The competent cells are stored at -80\textcelsius. Thaw the frozen cell on ice for 15 minutes and take 50$\mu$L into a 15mL Falcon round-bottom tube (BD) by pipetting. Add 0.5$\mu$L of transgenic plasmid (50-100ng) into the bacteria and incubate on ice for 30 minutes. Then put the tube into 42\textcelsius~water bath for 30 seconds as heat shock. Put the tube back on ice for another 2 minutes, then add 450$\mu$L of S.O.C medium (CloneTech). Incubate in 37\textcelsius~shaker for 1.5 hours with the speed of 200rpm. Take 20$\mu$L and 100$\mu$L of the bacterial culture and spread on the LB 0.1\% agar plate separately. Leave the plate up side down in an 37\textcelsius~incubator for over night. 
\section{Protein Extraction}
\subsection{Leaf Protein Extraction}
Add cOmplete protease inhibitor (Roche) into protein extraction buffer and make the final concentration to 1\%. Add every 100$\mu$L extraction buffer (containing protease inhibitor) per 100mg Arabidopsis leaf tissue. Use sterilised pellet pestle to grind with liquid nitrogen. \\
The recipe for protein extraction buffer is \\ 

\begin{tabular}[h]{c c}
	\hline
	\textsf{\textbf{Components}} & \textsf{\textbf{Components added(1L)}} \\
	\hline
	Tris-Base & 50g \\
	\ce{NaCl} & 150g \\
	EDTA & 5g \\
	\hline
\end{tabular}
\linebreak
\linebreak
Then adjust the pH value to 7.0.

\subsection{Seedling Protein Extraction}
We modify the method of \citet{tsugama2011rapid}. Pick 2~3 seedlings from the growth plate with tweezer and place them carefully at the bottom of a 1.5mL eppendorf tube. Add 100$\mu$L seedling lysis buffer. Then put the tube into 98\textcelsius and boil the sample for 10 minutes. Samples can be directly used for SDS PAGE gel loading after 10 minutes' boiling.\\
Seedling lysis buffer is prepared as following:\\

\begin{tabular}{c c c}
	\hline
	\textsf{\textbf{Components}} & \textsf{\textbf{Component Added(50mL)}} & \textsf{\textbf{Final Concentration}} \\
	\hline
	0.5M EDTA (pH 8.0) & 10mL & 0.1M \\
	1.0M Tris-\ce{HCl} (pH 6.8) & 6mL & 0.12M \\
	10\% SDS & 20mL & 4\% (w\textfractionsolidus v)\\
	100\% $\beta$-ME & 5.0 & 10\% (v\textfractionsolidus v) \\
	100\% Glycerol & 2.5mL & 5\% (v\textfractionsolidus v) \\
	Bromophenol Blue & 2.5mg & 0.005\% (w\textfractionsolidus v) \\
	\hline
\end{tabular}
\linebreak
\linebreak
We use Tris-Base to prepare 1.0M Tris-\ce{HCl} (pH 6.8) stock adjusting pH value with 0.1M \ce{HCl} solution rather than directly using Tris-\ce{HCl}. Directly dissolving Tris-\ce{HCl} can get lower pH value.

\subsection{Leaf Protein Extraction for enzymatic assay}
Using 100$\mu$L of extraction buffer for each 100mg leaf sample. Grind sample with autoclaved pestle in 1.5mL Eppendorf tube under 4\textcelsius. Rotate the sample under 4\textcelsius for 10 minutes. After rotation, the sample should be centrifuged for at least 10 minutes at 4\textcelsius with the speed of 13000 rpm. Collect the supernatant into a new 1.5mL Eppendorf tube after centrifugation and keep it on ice. For enzymatic assay experiments, the protein sample should be consumed freshly. Leaving the extract at -20\textcelsius for overnight will lose the activity of the enzymes.\\
For DEVDase and YVADase enzymatic assay, the general extraction buffer should be used:\\

\begin{tabular}[h]{l c}
	\hline
	\textbf{\textsf{Components}} & \textbf{\textsf{Final Concentration}} \\
	\hline
	DTT & 3mM \\
	PMSF & 100$\mu$M \\
	dd\ce{H2O} & to make up the volume\\
	\hline
\end{tabular}
\linebreak
\linebreak

\subsection{Protein Concentration Measurement}
To measure the concentration of protein in the extracts, we use Quick Start\texttrademark~Bradford 1$\times$ Dye Reagent (Bio-Rad). Prepare Bradford protein assay using 995$\mu$L of Bradford 1$\times$ reagent and 5$\mu$L of protein extracts into a 10mm$\times$10mm cuvette. Mix well and leave at room temperature for 10 minutes and measure the absorbence at 595nm using UV Spectrometer (eppendorf).\\
We use Pierce 660nm Protein Assay Kit (Thermo-Scientific) for urea-contained protein extracts. The maximum urea compatibility concentration reaches 8M according to the product manual. Each assay is made with 990$\mu$L of Pierce reagent and 10$\mu$L of protein extract into a 10mm$\times$10mm cuvette. Leave the assay at room temperature for 10 minutes and measure the absorbance at 660nm using UV Spectrometer.
\section{Enzymatic Assay Test}
\subsection{DEVDase Assay Test}
Get the protein extract according to the leaf protein extraction method for enzymatic assay. Protein extracts are incubated in a fluorescence-based assay microplate (Thermo-Scientific) with 2$\times$ DEVDase assay buffer at 30\textcelsius~for 30 minutes. Then add 50$\mu$M \ce{(Z-DEVD)2}-Rhodamine 110 (Bachem) and shake the plate at 37\textcelsius~for 10 seconds before reading using microplate fluorometer (DYNEX). Incubate the plate for another 30 minutes and take a reading every 3 minutes after start. Set the wavelength of excitation and emission to 485nm and 530nm.\\
For DEVDase enzymatic assay, the general extraction buffer should be used:\\

\begin{tabular}[h]{l c}
	\hline
	\textbf{\textsf{Components}} & \textbf{\textsf{Final Concentration}} \\
	\hline
	DTT & 3mM \\
	PMSF & 100$\mu$M \\
	dd\ce{H2O} & to make up the volume\\
	\hline
\end{tabular}
\linebreak
\linebreak
DEVDase Assay Buffer (2$\times$) is prepared in dd\ce{H2O} with the pH value 5.3, add half of the total assay volume.\\

\begin{tabular}{c c}
	\hline
	\textsf{\textbf{Compnents}} & \textsf{\textbf{Final Concentration (2$\times$)}} \\
	\hline
	\ce{NaCl} & 200mM \\
	\ce{CH3COONa} & 50mM \\
	DTT & 3mM \\
	\hline
\end{tabular}
\linebreak
\linebreak
In the assay, the working concentration of inhibitor CA-074 (Sigma-Alderich) in dd\ce{H2O} is 1mM, and $\beta$-Lactone (Sigma-Alderich) in dd\ce{H2O} is 50$\mu$M. For the control, use dd\ce{H2O} to make up the volume.
\subsection{LLVYase Assay Test}
Use LLVYase Assay Extraction Buffer to get the protein extracts for LLVYase assay test. Mix the extracts with the same assay buffer in a 96-well microplate and add 50$\mu$M Suc-LLVY-AMC (Enzo) into the assay. Shake the plate for 10 seconds at 37\textcelsius~and then incubate the plate in microplate fluorometer (DYNEX) for 30 minutes at 37\textcelsius. Measure the fluorescence every 3 minutes, set the wavelength for excitation and emission to 380nm and 460nm.

For LLVYase enzymatic assay, the extraction buffer is prepared using the following recipe:\\

\begin{tabular}[h]{l c}
	\hline
	\textbf{\textsf{Components}} & \textbf{\textsf{Final Concentration}} \\
	\hline
	Tris-\ce{HCl} & 50mM \\
	\ce{KCl} & 25mM \\
	\ce{NaCl} & 10mM \\
	ATP & 5mM \\
	dd\ce{H2O} & to make up the volume\\
	\hline
\end{tabular}
\linebreak
\linebreak
ATP should be added freshly before experiment. Adjust the pH value to 7.0, the LLVYase buffer is preferably prepared before using. Keep storing at 4\textcelsius.

\subsection{YVADase Assay Test}
Use YVADase enzymatic assay extraction buffer and follow the leaf protein extraction method to get the protein extracts. Incubate the protein extracts with YVADase assay buffer and 200$\mu$M Ac-YVAD-AMC substrate for 1 hour at 30\textcelsius. Shake the microplate for 10 seconds at 37\textcelsius~before incubation. Measure the fluorescence by using microplate fluorometer (DYNEX) and read every 3 minutes. The wavelength for excitation and emission is set to 380nm and 460nm.\\
YVADase enzymatic assay extraction buffer and YVADase Assay Buffer are prepared based on the method published by \cite{hatsugai2004plant}.\\
YVADase extraction buffer:\\

\begin{tabular}{c c}
	\hline
	\textbf{\textsf{Components}} & \textbf{\textsf{Final Concentration}} \\
	\hline
	\ce{CH3COONa} & 50mM \\
	\ce{NaCl} & 50mM \\
	EDTA & 1mM \\
	\hline
\end{tabular}
\linebreak
\linebreak
YVADase assay buffer: \\

\begin{tabular}{c c}
	\hline
	\textbf{\textsf{Components}} & \textbf{\textsf{Final Concentration}} \\
	\hline
	\ce{CH3COONa} & 20mM \\
	EDTA & 0.1mM \\
	DTT & 100mM \\
	\hline
\end{tabular}
\linebreak
\linebreak
The pH value of both extraction buffer and assay buffer are 5.5.
\section{Western Blotting}
\subsection{SDS PAGE Gel}
For common western-blotting experiments, we use general SDS PAGE (10\%) gel to analyse the protein samples.\\
The separating gel (10\% Acrylamide):\\

\begin{tabular}[h]{l c}
	\hline
	\textbf{\textsf{Components}} & \textbf{\textsf{Volume Added}} \\
	\hline
	dd\ce{H2O} & 1.8mL \\
	30\% Acrylamide & 1.5mL \\
	Tris-\ce{HCl} (pH 8.8) & 1.2mL \\
	10\% SDS solution & 50$\mu$L \\
	10\% APS solution & 15$\mu$L \\
	TEMED & 5$\mu$L \\
	\hline
\end{tabular}
\linebreak
\linebreak
The stacking gel (4\% Acrylamide): \\

\begin{tabular}[h]{l c}
	\hline
	\textbf{\textsf{Components}} & \textbf{\textsf{Volume Added}} \\
	\hline
	dd\ce{H2O} & 1.83mL \\
	30\% Acrylamide & 0.39mL \\
	Tris-\ce{HCl} (pH 6.8) & 0.75mL \\
	10\% SDS solution & 30$\mu$L \\
	10\% APS solution & 30$\mu$L \\
	TEMED & 3$\mu$L \\
	\hline
\end{tabular}
\linebreak
\linebreak
For smaller size proteins ($\leqslant$ 40kD), we modify the general SDS PAGE gel by adding urea instead of water. The recipe follows the method by \cite{hofius2009autophagic}.\\
The separating gel (15\% Acrylamide): \\

\begin{tabular}[h]{l c}
	\hline
	\textbf{\textsf{Components}} & \textbf{\textsf{Volume Added}} \\
	\hline
	Urea & 1.8g \\
	30\% Acrylamide & 2.5mL \\
	1.5M Tris-\ce{HCl} (pH 8.8) & 1.25mL \\
	10\% SDS solution & 50$\mu$L \\
	10\% APS solution & 50$\mu$L \\
	TEMED & 3.0$\mu$L \\
	\hline
\end{tabular}
\linebreak
\linebreak
The stacking gel (4\% Acrylamide): \\

\begin{tabular}[h]{l c}
	\hline
	\textbf{\textsf{Components}} & \textbf{\textsf{Volume Added}} \\
	\hline
	dd\ce{H2O} & 1.4mL \\
	30\% Acrylamide & 0.33mL \\
	1M Tris-\ce{HCl} (pH 6.8) & 0.25mL \\
	10\% SDS solution & 20$\mu$L \\
	10\% APS solution & 20$\mu$L \\
	TEMED & 2.0$\mu$L \\
	\hline
\end{tabular}
\subsection{Sampling and gel running condition}
Before loading the protein sample, mix the protein sample and Protein Loading Buffer (2$\times$), put the mixture into dry bath and heat at 95\textcelsius for 5 minutes. The Protein Loading Buffer (2$\times$) is prepared as the following recipe, and stored at -20\textcelsius:\\

\begin{tabular}[h]{l c c }
	\hline
	\textbf{\textsf{Components}} & \textbf{\textsf{Volume Added(50mL)}} & \textbf{\textsf{Final concentration}}\\
	\hline
	1M Tris-\ce{HCl} (pH 6.8) & 4.0mL & 80mM \\
	20\% SDS & 5mL & 2.0\% \\
	Glycerol (Autoclaved) & 5mL & 10\% \\
	0.1\% Bromophenol Blue & 300$\mu$L & 0.0006\% \\
	1M DTT & 5mL & 0.1M \\
	dd\ce{H2O} & 30.7mL & \\
	\hline 
\end{tabular}
\linebreak
\linebreak
Load protein sample with Precision Plus Protein Dual Color Standards (Bio-Rad), add approximately 500$\mu$L SDS PAGE running buffer into the electrophoresis chamber. Use 80V for the first 20 minutes and then increase the voltage to 100V and run for 150 minutes.\\
Use PVDF blotting membrane (GE Healthcare Life Sciences) for protein transferring. Transfer the membrane at 4\textcelsius~for 1 hour, set the voltage to 100V.\\
The buffers are prepared based on the following recipes.\\
SDS PAGE running buffer (1$\times$):\\

\begin{tabular}[h]{l c c }
	\hline
	\textbf{\textsf{Components}} & \textbf{\textsf{Component Added(1L)}} & \textbf{\textsf{Final concentration}}\\
	\hline
	Tris-\ce{HCl} & 3.03g & 25mM \\
	Glycine & 14.44g & 192mM \\
	SDS & 1.0g & 0.1\% \\
	\hline 
\end{tabular}
\linebreak
\linebreak
All the components are dissolved in dd\ce{H2O}, usually we prepare 10$\times$ running buffer for stock, and dilute to 1$\times$ when use.\\
SDS PAGE membrane transferring buffer (1$\times$):\\

\begin{tabular}[h]{l c c }
	\hline
	\textbf{\textsf{Components}} & \textbf{\textsf{Component Added(1L)}} & \textbf{\textsf{Final concentration}}\\
	\hline
	Tris-Base & 5.8g & 50mM \\
	Glycine & 2.9g & 40mM \\
	10\% SDS solution & 3.7mL & 0.037\% \\
	dd\ce{H2O} & 500mL & \\
	100\% Methanol & 200mL & 20\%(v\textfractionsolidus v) \\
	\hline
\end{tabular}
\linebreak
\linebreak
Then add dd\ce{H2O} to 1L for transferring. \\
An alternative method to transfer the protein from SDS PAGE gel to PVDF membrane is to use Pierce G2 Fast Blotter machine (Thermo-Scientific), with the use of Pierce 1-Step Transfer Buffer (Thermo-Scientific) for transferring. The whole protocol is based on the Thermo-Scientific user manual.

\subsection{Protein detecting}
We use 3\%~ BSA-PBS-T buffer to block the Western membrane, shake at 4\textcelsius with the speed of 60rpm for overnight. When applying primary and secondary antibodies, we add antibody into 2\%~BSA-PBS-T buffer. The concentration of antibody follows the instructions from the manufacturer. Immerse the membrane into buffer with antibody and incubate on a shaker at room temperature for 1 hour with the speed of 50rpm. Wash three times with PBS-T three times and 10 minutes each using the same shaking condition. Use enhanced chemilumiscent (ECL) substrate kit (Thermo-Scientific) to develop in dark for 1 minute. Use X-ray film (Thermo-Scientific) for photographing in dark room. The exposure time varies.\\
For faster developing, we mix and balance two different ECL substrates with different sensitivity, SuperSignal West Pico PLUS Substrate and SuperSignal West Femto Substrate (Thermo-Scientific). The standard ratio of Pico PLUS and Femto substrate is 14:1.

\section{GUS tissue staining}
Collect tissue samples into a new 1.5mL Eppendorf tube. Add 100$\mu$L pre-chilled 90\% acetone and get sample fully immersed. Incubate at room temperature for 20 minutes. Wash with staining buffer for 3 times on ice. Discard staining buffer after washing and then add newly prepared staining solution (staining buffer containing X-Gluc substrate) and infiltrate on ice under vacuum condition using vacuum pump and desiccator for 15 minutes. Use film to seal the tube to avoid evaporation of staining solution then pack the samples tubes in aluminium foil to leave the stained sample in dark for overnight (no more than 24 hours).\\
\linebreak
After staining, use dd\ce{H2O} to rinse the sample, then use 70\% ethanol to extract chlorophyll if necessary. The sainted samples can be stored at room temperature for over 2 months.\\

\section{DAB histochemical staining}
Arabidopsis leaf DAB staining is modified from the original method published by \cite{daudi2012detection}. Preparing 0.1\% 3,3'-Diaminobenzidine (DAB) staining solution. For every 50mL of volume, weigh 50mg of DAB powder (Sigma-Aldrich) and add 5mL of dd\ce{H2O}. Then add 2.5mL 0.2M \ce{HCl} to dissolve the DAB powder. Re-add dd\ce{H2O} to 35mL and then adjust the pH value to 6.5 using 0.2M \ce{Na2HPO4}. Finally add dd\ce{H2O} to exact 50mL. Prepare this staining solution freshly before each experiment, pack it with aluminium foil and leave it on ice.\\
\linebreak
Use the fresh plant tissue sample and soak it with DAB staining solution. Put it into a desiccator and treat the sample with vacuum for at least 1 minute. Then cover it with aluminium foil and incubate on a shaker at room temperature with the speed of 60rpm. The total incubation time varies from 6 to 8 hours in most cases. The incubation time is adjustable depending on the staining condition.\\
\linebreak
To wash the chlorophyll after staining, prepare the DAB washing buffer as following (per 50mL):\\

\begin{tabular}[h]{l c}
	\hline
	\multicolumn{1}{c}{\textsf{\textbf{Compnents}}} & \textsf{\textbf{Volumn Added (mL)}} \\
	\hline
	100 \% Ethanol & 30 \\
	Acetic Acid Glacial & 10 \\
	Glycerol & 10 \\
	\hline
\end{tabular}
\linebreak
\linebreak
Wash the samples under 95\textcelsius for at least 15 minutes, depending on the washing result. After this step, the chlorophyll should be washed off from the tissue.\\
\section{Ion Leakage Test}
Harvest Arabidopsis plant and cut the leaves with scalpel blade. We use cork borer to punch out leaf disks (4mm $\times$ 4mm). Use 24-well culture plate (Corning) and add 2mL MilliQ water into the wells. Place leaf disks carefully using tweezers into the wells, totally 3~5 disks in each well. Then gently shake the plate ($\approx$40rpm) for 1 hour before measuring to make sure it reaches ion-environmental stability. For ion leakage measurement, we use LAQUAtwin portable conductivity meter (HORIBA) to measure the ion abundance in each well. Take 200$\mu$L from each well and get the reading of the sum of the leaf disks in the well.
\section{Protoplast Isolation}
The method we use to isolate Arabidopsis protoplasts is based on \citet{wu2009tape} and \citet{yoo2007arabidopsis}. The leaves for isolation are 4-5 weeks old under short-day growth condition. The optimal size of one leaf is 3.0cm$\times$1.5cm. Cut the leaves with scalpel blade, and use thick floor making tape (Shamrocks) to stabilise the upper epidermal surface. For the lower epidermis, we use Scotch invisible tape (3M) to adhere on the surface. Press gently and then peel off the invisible tape to let the spongy mesophyll cells exposed. Put the lower epidermis-free leaves into a clean Petri dish and immerse the leaves into 10mL enzyme solution. Shake the Petri dish at room temperature with the speed of 40rpm, for totally 1$\sim$2 hours, until the cells are mostly isolated from the leaves. Collect the cells into a 50mL centrifuge tube (Corning) and centrifuge for 3 minutes at 100rcf. Then wash and re-suspend twice with 25mL pre-chilled W5 washing buffer and use the same condition for centrifugation. Incubate on ice for 30 minutes. Count and calculate the number and abundance of protoplasts using hemocytometer under dissecting microscope. Then centrifuge for 3 minutes at 100rcf and carefully discard the supernatant. Then re-suspend the protoplasts with MMG solution and keep the cell stored at room temperature.\\
We prepare the enzyme solution used for digesting the mesophyll cell wall as the following recipe. For each Petri dish we use 10mL of enzyme solution, \\

\begin{tabular}{c c c}
	\hline
	\textsf{\textbf{Components}} & \textsf{\textbf{Component added (10mL)}} & \textsf{\textbf{Final Concentration}} \\
	\hline
	Manitol & 0.729g & 0.4M \\
	\ce{CaCl2} & 0.011g & 10mM \\
	\ce{KCl} & 0.015g & 220mM \\
	MES & 0.039g & 20mM \\
	\hline	
\end{tabular}
\linebreak
\linebreak
Adjust the pH value to 5.7 before adding enzyme. For the complete enzyme solution, add the following:\\

\begin{tabular}{c c c}
	\hline
	\textsf{\textbf{Components}} & \textsf{\textbf{Component added (10mL)}} & \textsf{\textbf{Final Concentration}} \\
	\hline
	Cellulase 'Onozuka' R-10 & 0.10g & 1\% \\
	Macerozyme R-10 & 0.025g & 0.25\% \\
	BSA & 0.01g & 0.1\% \\
	\hline
\end{tabular}
\linebreak
\linebreak
Pre-made enzyme solution stock can be stored at -20\textcelsius, thaw on ice for overnight before use.\\
W5 Solution is prepared and adjust pH value to 5.7.\\

\begin{tabular}{c c c}
	\hline
	\textsf{\textbf{Components}} & \textsf{\textbf{Component added (500mL)}} & \textsf{\textbf{Final Concentration}} \\
	\hline
	\ce{NaCl} & 4.5g & 154mM \\
	\ce{CaCl2} & 6.93g & 125mM \\
	\ce{KCl} & 0.19g & 5mM \\
	Glucose & 0.45g & 5mM \\
	MES & 0.20g & 2mM \\
	\hline
\end{tabular}
\linebreak
\linebreak
MMg solution is prepared as the following description, with the pH value 5.7, is used for protoplasts re-suspending.\\ 

\begin{tabular}{c c c}
	\hline
	\textsf{\textbf{Components}} & \textsf{\textbf{Component added (500mL)}} & \textsf{\textbf{Final Concentration}} \\
	\hline
	Manitol & 36.43g & 0.4M \\
	\ce{MgCl2}$\cdot$\ce{6H2O} & 1.52g & 15mM \\
	MES & 0.39g & 4mM \\
	\hline
\end{tabular}
\section{Tools \& Software}
\subsection{Modelling Tool}
We use the Systems Biology Markup Language (SBML) (\url{http://sbml.org/Main_Page}) tool for building and doing basic numerical simulation of the models.